Generating Images from Captions\\ with Attention

### 2015-12-28 rebuttal.txt

Dear reviewers,
We thank you for very constructive reviews.

----
Reviewer 1

Q. It would also be nice to know how their align function compares to the standard content-based attention.

A. Not sure what to write to him/her. Not clear what reviewer means by "standard content-based attention".

----
Reviewer 2

Q. The results of "picture of a cat" vs. "picture of a dog" highlight my concern - I see no noticeable difference between the two sets of generated images.

A. Yes this example was meant to highlight the limitation of our model.

Q. The use of SSI and retrieval for comparison of the generative models is interesting, but I worry that the regime in which these models operate (SSI 0-0.2) is not a place where SSI is really useful or particularly interpretable - is a relative gain of 0.08 to 0.156 immense, or "in the noise". What is the standard deviation of the measurements for each row?

A. We agree that SSI results may not be particularly interpretable, however it was one of the only good ways to quantitatively compare performances of LAPGAN and our model that we could think of. The standard deviation for each model is around 0.1

Good quantitative evaluation of generative models still remains an open problem that was recently adressed in Theis et al. 2015.

Q. Given the recent (e.g. under submission in this conference!) improvements to generative models, I would expect this work will be extended to much higher quality in the near future. This paper lays solid groundwork for that, and is interesting in its own right, though the generated image quality is the main a limiting factor in giving a higher score.

A. As for the recent work on Generative Adversarial Networks (GANs) by Radford et al. 2015, their model was trained on a very narrow domain of images, for example millions of images of just bedrooms from LSUN dataset, where it is not clear whether the model is overfitting or not. In comparison, Microsoft COCO is much smaller and much more diverse dataset. Conditioning the model on captions provides a clear qualitative way to see whether the model has some notion of generalization. Being able to generalize to weird and novel captions not present in dataset is in itself a very challenging problem. At the same time, we hope that other researchers will try to come up with better generative models for this task.

----
Reviewer 3

Q. In the experiments, the size of the image is quite small (i.e 32 by 32). This means that the groundtruth images have already been blurred before the training of the model. This might be one of the reasons why the generated images are blurry. Can you train your model on images with common sizes (e,g, 100 by 100 or even 224 by 224)? Is there any obstacle to overcome for the proposed model to handle larger size of images than 32 by 32?

A. The images were resized to 32x32 dimension using nearest neighbor interpolation which doesn't make images blurry. The image size is not a limiting factor of the model, however it takes a bit more than a week to train the model on 32x32 images using Nvidia Titan GPUs due to large size of the model (both in depth and in time). Due to time constraints, we made the dimension of images in the dataset consistent with other popular tiny images datasets (CIFAR-10 and CIFAR-100).

Q. How does the model perform without the post-processing GAN model quantitatively, compared to other models with GAN shown in Table 1?

The results in Table 1 are shown without the post-processing GAN step. With post-processing step, where reconstruction error is the difference between sharpened images and real images instead of the difference between blurry images and real images, the ranking results become much worse. Median rank drops from 31 to 50, where ranking essentially becomes random. The bad quality of pixel-wise error motivated us to try better image similarity metrics such as SSI. In comparison SSI drops only by 0.02 points after sharpening images.

Q. It would be great if GAN post-processing step is merged into the model shown in Figure 2 so that the whole model can be trained and tested in an end-to-end way.

A. We tried combining VAE and GAN cost functions so that the model could be trained in an end-to-end fashion on CIFAR-10 and MS COCO datasets. We didn't have any success in that because the model started emphasizing GAN objective function and the samples started looking more like the samples from original GAN model from Goodfellow et al. 2014. Scaling both objectives and doing other tricks didn't help either. Note that Lotter et al. 2015 (Unsupervised Learning of Visual Structure using Predictive Generative Network submitted to this conference) have also tried combining both objectives in the similar way and had a limited success.

We also tried experimenting with other types of reconstruction error, for example in Fourier domain, all with no major success. Generating sharp and very realistic images from autoencoder without overfitting is a very hard problem and is part of an ongoing research (see Mathieu et al. 2015 Deep multi-scale video prediction beyond mean square error; Ridgeway et al. 2015 Learning to generate images with perceptual similarity metrics all submitted to this conference).

Q. In Eqn (15), only one sample is used for parameter learning. Will more samples make a difference in the learning process?

A. We would expect that using more samples would improve the lower bound of log likelihood as well as the quality of generated samples, which was shown recently in Burda et al. 2015 Importance Weighted Autoencoders (also submitted to this conference). However, using more samples would increase the training time and in our case training already takes quite a while on Nvidia Titan GPUs.

### 2015-12-30 rebuttal.txt

We thank all reviewer for their valuable reviews.

Reviewer 2

Regarding the results of "picture of a cat" vs. "picture of a dog" with no noticeable difference:
Indeed, when swapping two objects that are visually similar, it is difficult to discriminate solely from the generated samples. This example was meant to highlight a limitation of our model in that it has difficulty generating the fine-grained details of objects.

The use of SSI and retrieval for comparison:
We agree that SSI results may not be particularly interpretable, however it was one of the only good ways to quantitatively compare performances of LAPGAN and our model that we could think of. We note that good quantitative evaluation of generative models still remains an open problem as was recently discussed in Theis et al. 2015.

The standard deviation of SSI scores for variational models is 0.1 and the standard deviation for LAPGAN is 0.08. We will add these numbers to the paper.

On the the recent improvements to generative models and the generated image quality remaining the main a limiting factor:
We agree that there has been a lot of recent work on improving generative models. However, even today, generating sharp and globally consistent images of arbitrary scenes remains an open problem.

For example, in the recent work on Generative Adversarial Networks (GANs) by Radford et al. 2015, 
they train their model on a very narrow domain of images -- millions of images of just 
bedroom scenes from LSUN bedroom dataset. In this setting, it is may not clear how much overfitting takes place. 
In comparison, Microsoft COCO is a far more diverse dataset. Conditioning the model on 
novel captions provides a clear qualitative way to evaluate whether the model has some notion of generalization. 
Being able to generalize to novel captions not present in dataset, such as 
"A herd of elephants flying
in the blue skies" is in itself a very challenging problem. 
At the same time, we also hope that other researchers will try to come up with better generative models for this task.

Reviewer 3

In regard to small size images and training images with more common sizes: 
The images were resized to 32x32 dimension using bi-cubic interpolation and the resulting images do not look 
blurry. The image size is not a limiting factor of the model, however, it takes about a week 
to train our model on 32x32 images on a single Nvidia TitanX GPU due to large size of the model 
(both in depth and in time). Due to time constraints, we made the dimension of images in the dataset consistent with other popular tiny images datasets (CIFAR-10 and CIFAR-100). 
We also believe that scaling our model up to modeling 64x64 or 100x100 images 
will not necessarily significantly improve the quality of generated images.

Model performance without the post-processing GAN step:   
The results in Table 1 are shown without the post-processing GAN step. We found that with the post-processing GAN step, the ranking results became much worse. Median rank drops from 31 to 50, in which 
case the ranking essentially becomes random. The bad quality of pixel-wise error motivated 
us to try better image similarity metrics such as SSI. In comparison, SSI drops only by 0.02 points 
after sharpening images.

In regard to merging GAN post-processing step into the whole model:
We tried combining VAE and GAN cost functions so that the model could be trained in an end-to-end fashion on CIFAR-10 and MS COCO datasets. 
So far, we did not have much success in that because the model started emphasizing GAN objective function and the samples started to look more like the samples from the GAN model. Scaling both objectives and doing other tricks 
did not help either. Note that Lotter et al. 2015 (Unsupervised Learning of Visual Structure using Predictive Generative Network submitted to this conference) have also tried combining both objectives in a similar way and had a limited success.

We also tried experimenting with other types of reconstruction error, for example in Fourier domain, all with no major success so far. Generating sharp and very realistic images remains challenging and is part of an ongoing research (see Mathieu et al.; Ridgeway et al. 2015 all submitted to this conference).

Eq (15): 1 vs. many samples:
We would expect that using more samples could improve the lower bound on the log-likelihood 
as well as the quality of generated samples, especially when using importance sampling as 
was shown recently in Burda et al. 2015. However, using more samples would increase the training 
time, which in our case already takes quite a while (using TitanX GPUs).

### 2015-12-30 rebuttal.txt

We thank all reviewer for their valuable reviews.

Reviewer 1:
Thank you for your review, but we were not quite sure what the reviewer meant by the standard content-based attention. In our paper, we compared the performance of our model to the DRAW model conditioned on captions
without attention and the DRAW model conditioned on
the skipthought vectors of Kiros et al., 2015.
We generally found that the
quality of generated samples was similar among different variants of conditional DRAW models.

Reviewer 2:

@@

The standard deviation of SSI scores for variational models is 0.1 and the standard deviation for LAPGAN is 0.08. We will add these numbers to the paper.

On the the recent improvements to generative models and the generated image quality remaining the main a limiting factor:
We agree that there has been a lot of recent work on improving generative models. However, even today, generating sharp and globally consistent images of arbitrary scenes remains an open problem.

For example, in the recent work on Generative Adversarial Networks (GANs) by Radford et al. 2015, 
they train their model on a very narrow domain of images -- millions of images of just 
bedroom scenes from LSUN bedroom dataset. In this setting, it is may not clear how much overfitting takes place. 
In comparison, Microsoft COCO is a far more diverse dataset. Conditioning the model on 
novel captions provides a clear qualitative way to evaluate whether the model has some notion of generalization. 
Being able to generalize to novel captions not present in dataset, such as 
"A herd of elephants flying
in the blue skies" is in itself a very challenging problem. 
At the same time, we also hope that other researchers will try to come up with better generative models for this task.

Reviewer 3:

In regard to small size images and training images with more common sizes: 
The images were resized to 32x32 dimension using bi-cubic interpolation and the resulting images do not look 
blurry. The image size is not a limiting factor of the model, however, it takes about a week 
to train our model on 32x32 images on a single Nvidia Titan GPU due to large size of the model 
(both in depth and in time). Due to time constraints, we made the dimension of images in the dataset consistent with other popular tiny images datasets (CIFAR-10 and CIFAR-100). 
We also believe that scaling our model up to modeling 64x64 or 100x100 images 
will not necessarily significantly improve the quality of generated images.

@@

Model performance without the post-processing GAN step:   
The results in Table 1 are shown without the post-processing GAN step. We found that with the post-processing GAN step, the ranking results became much worse. Median rank drops from 31 to 50, in which 
case the ranking essentially becomes random. The bad quality of pixel-wise error motivated 
us to try better image similarity metrics such as SSI. In comparison, SSI drops only by 0.02 points 
after sharpening images.

In regard to merging GAN post-processing step into the whole model:
We tried combining VAE and GAN cost functions so that the model could be trained in an end-to-end fashion on CIFAR-10 and MS COCO datasets. 
So far, we did not have much success in that because the model started emphasizing GAN objective function and the samples started to look more like the samples from the GAN model. Scaling both objectives and doing other tricks 
did not help either. Note that Lotter et al. 2015 (Unsupervised Learning of Visual Structure using Predictive Generative Network submitted to this conference) have also tried combining both objectives in a similar way and had a limited success.

We also tried experimenting with other types of reconstruction error, for example in Fourier domain, all with no major success so far. Generating sharp and very realistic images remains challenging and is part of an ongoing research (see Mathieu et al.; Ridgeway et al. 2015 all submitted to this conference).

Eq (15): 1 vs. many samples:
We would expect that using more samples could improve the lower bound on the log-likelihood 
as well as the quality of generated samples, especially when using importance sampling as 
was shown recently in Burda et al. 2015. However, using more samples would increase the training 
time, which in our case already takes quite a while (using Titan GPUs).

### 2015-12-31 rebuttal.txt

We thank all reviewer for their valuable feedback.

Reviewer 1:
Thank you for your review. We were not quite sure what the reviewer meant by the standard content-based attention. In our paper, we compared the performance of our model to the DRAW model conditioned on captions
without attention and the DRAW model conditioned on the skipthought vectors of Kiros et al., 2015.
We generally found that the quality of generated samples was similar among different variants of conditional DRAW models.

@@

Reviewer 2:

Regarding the results of "picture of a cat" vs. "picture of a dog" with no noticeable difference:
Indeed, when swapping two objects that are visually similar, it is difficult to discriminate solely from the generated samples. This example was meant to highlight a limitation of our model in that it has difficulty generating the fine-grained details of objects.

The use of SSI and retrieval for comparison:
We agree that SSI results may not be particularly interpretable. However, it was one of the only good ways to quantitatively compare performances of LAPGAN and our model that we could think of. We note that good quantitative evaluation of generative models still remains an open problem as was recently discussed in Theis et al. 2015.

@@

The standard deviation of SSI scores for variational models is 0.1 and the standard deviation for LAPGAN is 0.08. We will add these numbers to the paper.

On the recent improvements to generative models and the quality of generated images:
We agree that there has been a lot of recent work on improving generative models. However, even today, generating sharp and globally consistent images of arbitrary scenes remains an open problem.

@@

For example, in the recent work on Generative Adversarial Networks (GANs) by Radford et al. 2015, they train their model on a very narrow domain of images -- millions of images of just 
bedroom scenes from LSUN bedroom dataset. In this setting, it is may not clear how much overfitting takes place. 
In comparison, Microsoft COCO is a far more diverse dataset. Conditioning the model on 
novel captions provides a clear qualitative way to evaluate whether the model has some notion of generalization. 
Being able to generalize to novel captions not present in dataset, such as 
"A herd of elephants flying in the blue skies" is in itself a very challenging problem. At the same time, we also hope that other researchers will try to come up with better generative models for this task.

Reviewer 3:

In regard to training on small size images:
The images were resized to 32x32 using bi-cubic interpolation and the resulting images did not look blurry. The image size is not a limiting factor of the model. However, even on a high-end GPU it takes about a week 
to train our model on 32x32 images due to the large size of the model 
(both in depth and in time). Due to time constraints, we made the dimension of images in the dataset consistent with other popular tiny images datasets (CIFAR-10 and CIFAR-100). 
We also believe that scaling our model up to modeling 64x64 or 100x100 images 
will not necessarily significantly improve the quality of generated images.

Model performance without the post-processing GAN step:   
The results in Table 1 are shown without the post-processing GAN step. We found that with the post-processing GAN step, the ranking results became much worse. Median rank dropped from 31 to 50, in which 
case the ranking essentially became random. The bad quality of pixel-wise error motivated 
us to try better image similarity metrics such as SSI. In comparison, SSI drops only by 0.02 points 
after sharpening images.

In regard to merging GAN post-processing step into the whole model:
We tried combining VAE and GAN cost functions so that the model could be trained in an end-to-end fashion on CIFAR-10 and MS COCO datasets. 
So far, we did not have much success because the model started emphasizing GAN objective function and the samples started to look more like the samples from the GAN model. Scaling both objectives and doing other tricks 
did not help either. Note that Lotter et al. 2015 (Unsupervised Learning of Visual Structure using Predictive Generative Network submitted to this conference) have also tried combining both objectives in a similar way and had a limited success.

We have also tried experimenting with other types of reconstruction error, for example in Fourier domain, all with no major success so far. Generating sharp and very realistic images remains challenging and is part of an ongoing research (see Mathieu et al.; Ridgeway et al. 2015 all submitted to this conference).

Eq (15): 1 vs. many samples:
We would expect that using more samples could improve the lower bound on the log-likelihood 
as well as the quality of generated samples, especially when using importance sampling as 
was recently demonstrated by Burda et al. 2015. However, using more samples would increase the training 
time, which in our case already takes quite a while.

### 2016-01-04 rebuttal.txt

We thank all reviewers for their valuable feedback.

Reviewer 1:

Thank you for your review. We were not quite sure what you meant by the standard content-based attention. In our paper, we compared the performance of our model to the DRAW model conditioned on captions without attention and the DRAW model conditioned on the skipthought vectors of Kiros et al., 2015. We generally found that the quality of generated samples was similar among different variants of conditional DRAW models.

@@

Reviewer 2:

Regarding the results of "picture of a cat" vs. "picture of a dog" with no noticeable difference:

Indeed, when swapping two objects that are visually similar, it is difficult to discriminate solely from the generated samples. This example was meant to highlight a limitation of our model in that it has difficulty generating the fine-grained details of objects.

The use of SSI and retrieval for comparison:

We agree that SSI results may not be particularly interpretable. However, it was one of the only good ways to quantitatively compare performances of LAPGAN and our model that we could think of. We note that good quantitative evaluation of generative models still remains an open problem as was recently discussed in Theis et al. 2015. 
The standard deviation of SSI scores for variational models is 0.1 and the standard deviation for LAPGAN is 0.08. We will add these numbers to the paper.

On the recent improvements to generative models and the quality of generated images:

We agree that there has been a lot of recent work on improving generative models. However, even today, generating sharp and globally consistent images of arbitrary scenes remains an open problem. For example, in the recent work on Generative Adversarial Networks (GANs) by Radford et al. 2015, they train their model on a very narrow domain of images -- millions of images of just bedroom scenes from LSUN bedroom dataset. In this setting, it is not clear how much overfitting takes place. In comparison, Microsoft COCO is a far more diverse dataset. Conditioning the model on novel captions provides a clear qualitative way to evaluate whether the model has some notion of generalization. Being able to generalize to novel captions not present in dataset, such as "A herd of elephants flying in the blue skies" is in itself a very challenging problem. At the same time, we also hope that other researchers will try to come up with better generative models for this task.

@@

Reviewer 3:

In regard to training on small size images:

The images were resized to 32x32 using bi-cubic interpolation and the resulting images did not look blurry. The image size is not a limiting factor of the model. However, even on a high-end GPU it takes about a week to train our model on 32x32 images due to the large size of the model (both in depth and in time). Due to time constraints, we made the dimension of images in the dataset consistent with other popular tiny images datasets (CIFAR-10 and CIFAR-100). We also believe that scaling our model up to modeling 64x64 or 100x100 images will not necessarily significantly improve the quality of generated images.

Model performance without the post-processing GAN step:

The results in Table 1 are shown without the post-processing GAN step. We found that with the post-processing GAN step, the ranking results became much worse. Median rank dropped from 31 to 50, in which case the ranking essentially became random. The bad quality of pixel-wise error motivated us to try better image similarity metrics such as SSI. In comparison, SSI drops only by 0.02 points after sharpening images.

In regard to merging GAN post-processing step into the whole model:

We tried combining VAE and GAN cost functions so that the model could be trained in an end-to-end fashion on CIFAR-10 and MS COCO datasets. So far, we did not have much success because the model started emphasizing GAN objective function and the samples started to look more like the samples from the GAN model shown in Goodfellow et. al. 2014. Scaling both objectives and doing other tricks did not help either. Note that Lotter et al. 2015 (Unsupervised Learning of Visual Structure using Predictive Generative Network submitted to this conference) have also tried combining both objectives in a similar way and had a limited success.

We have also tried experimenting with other types of reconstruction error, for example in Fourier domain, all with no major success so far. Generating sharp and very realistic images without overfitting remains challenging and is part of an ongoing research (see Mathieu et al.; Ridgeway et al. 2015 all submitted to this conference).

Eq (15): 1 vs. many samples:

We would expect that using more samples could improve the lower bound on the log-likelihood as well as the quality of generated samples, especially when using importance sampling as was recently demonstrated by Burda et al. 2015. However, using more samples would increase the training time, which in our case already takes quite a while.

### 2016-02-25 iclr-paper-new.tex
small changes for final revision

The terms in the variational lower bound Eq. \ref{eq:varbound} can be rearranged using the law of total expectation. Therefore, the variational bound $\loss$ is calculated as follows:
\begin{align}
\label{eq:loss}
\loss =  &\expectation_{Q(\Lat_{1:T}\given\icaption,\oimage)}\left[ \log p(\oimage\given\icaption,\Lat_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\Lat_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\Lat_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The expectation can be approximated by $\numSamples$ Monte Carlo samples $\LatSample_{1:T}$ from $\post(\Lat_{1:T}\given\icaption, \oimage)$:
\begin{align}
\label{eq:loss_mc}
\loss \approx  &\frac{1}{\numSamples}\sum_{\sampleIdx=1}^\numSamples\left[ \log p(\oimage\given\icaption,\LatSample^\sampleIdx_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The model can be trained using stochastic gradient descent. 
In all of our experiments, we used only a single sample 
from $\post(\Lat_{1:T}\given\icaption, \oimage)$ for parameter learning.
Training details, hyperparameter settings,
and the overall model architecture are specified in Appendix B. 
We will also release our code with pretrained models.

@@

\begin{table}[!t]
\vspace{-0.3in}
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c c}
\hline
\multicolumn{7}{c}{\textbf{Microsoft COCO (prior to sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Retrieval} & \multicolumn{1}{c}{Image Similarity} \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI}\\ %& \textbf{Feature Distance} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 \\ % & 6.89 \\ % - & - & - & - & - & 0.08
\hline
Fully-Conn VAE & 1.0 & 6.6 & 12.0 & 53.4 & 47 & 0.156 \\ %& 6.11 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv-Deconv VAE & 1.0 & 6.5 & 12.0 & 52.9 & 48 & 0.164 \\ %& 6.32 \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
skipthoughtDRAW & 2.0 & 11.2 & 18.9 & 63.3 & 36 & 0.157 \\ %& 6.93 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
noalignDRAW & 2.8 & 14.1 & 23.1 & 68.0 & 31 & 0.155 \\ %& 7.01 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
alignDRAW & 3.0 & 14.0 & 22.9 & 68.5 & 31 & 0.156 \\ %& 6.99 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\caption{Retrieval results of different models. 
\textbf{R@K} is Recall@K
    (higher is better). \textbf{Med} {\it r} is the median rank (lower is better). 
    \textbf{SSI} is Structural Similarity Index, which is between $-1$ and $1$ 
    (higher is better).
}
\label{tab:results}
\vspace{-0.1in}
\end{table}

>>>>

The terms in the variational lower bound Eq. \ref{eq:varbound} can be rearranged using the law of total expectation. Therefore, the variational bound $\loss$ is calculated as follows:
\begin{align}
\label{eq:loss}
\loss =  &\expectation_{Q(\Lat_{1:T}\given\icaption,\oimage)}\left[ \log p(\oimage\given\icaption,\Lat_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\Lat_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\Lat_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The expectation can be approximated by $\numSamples$ Monte Carlo samples $\LatSample_{1:T}$ from $\post(\Lat_{1:T}\given\icaption, \oimage)$:
\begin{align}
\label{eq:loss_mc}
\loss \approx  &\frac{1}{\numSamples}\sum_{\sampleIdx=1}^\numSamples\left[ \log p(\oimage\given\icaption,\LatSample^\sampleIdx_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The model can be trained using stochastic gradient descent. 
In all of our experiments, we used only a single sample 
from $\post(\Lat_{1:T}\given\icaption, \oimage)$ for parameter learning.
Training details, hyperparameter settings,
and the overall model architecture are specified in Appendix B. 
The code is available at \url{https://github.com/emansim/text2image}.
%We will also release our code with pretrained models.

@@

\begin{table}[!t]
\vspace{-0.3in}
\begin{center}
\begin{tabulary}{\linewidth}{c || c c c c c || c c}
\hline
\multicolumn{7}{c}{\textbf{Microsoft COCO (prior to sharpening)}} \\
\hline
& \multicolumn{5}{c||}{Image Retrieval} & \multicolumn{1}{c}{Image Similarity} \\
%\cline{2-6}
\textbf{Model} & \textbf{R@1} & \textbf{R@5} & \textbf{R@10} & \textbf{R@50} & \textbf{Med r} & \textbf{SSI}\\ %& \textbf{Feature Distance} \\
\hline
\hline
LAPGAN & - & - & - & - & - & 0.08 $\pm$ 0.07 \\ % & 6.89 \\ % - & - & - & - & - & 0.08
\hline
Fully-Conn VAE & 1.0 & 6.6 & 12.0 & 53.4 & 47 & 0.156 $\pm$ 0.10  \\ %& 6.11 \\ % 0.688 & 4.58 & 8.74 & 46.832 & 54 & -1
Conv-Deconv VAE & 1.0 & 6.5 & 12.0 & 52.9 & 48 & 0.164 $\pm$ 0.10 \\ %& 6.32 \\ % 0.672 & 4.448 & 8.476 & 46.596 & 54 & 0.131
skipthoughtDRAW & 2.0 & 11.2 & 18.9 & 63.3 & 36 & 0.157 $\pm$ 0.11 \\ %& 6.93 \\ % 0.988 & 6.18 & 11.48 & 52.512 & 48 & 0.118
noalignDRAW & 2.8 & 14.1 & 23.1 & 68.0 & 31 & 0.155 $\pm$ 0.11 \\ %& 7.01 \\ % 1.0 & 6.124 & 11.18 & 52.112 & 48 & 0.114
alignDRAW & 3.0 & 14.0 & 22.9 & 68.5 & 31 & 0.156 $\pm$ 0.11 \\ %& 6.99 \\ % 0.924 & 6.216 & 11.184 & 52.492 & 48 & 0.115
\end{tabulary}
\end{center}
\caption{Retrieval results of different models. 
\textbf{R@K} is Recall@K
    (higher is better). \textbf{Med} {\it r} is the median rank (lower is better). 
    \textbf{SSI} is Structural Similarity Index, which is between $-1$ and $1$ 
    (higher is better).
}
\label{tab:results}
\vspace{-0.1in}
\end{table}
